### 2020-04-30 serial.tex
space

Our study also demonstrates that there are multiple serial-interval distributions that correspond to the same set of generation-interval and incubation period distributions depending on their correlations;
all of them can provide the correct link between $r$--\RR (\fref{rR}).
Conversely, this means that not explicitly accounting for their correlations can bias the estimate of the intrinsic generation-interval distribution from the serial-interval distribution.
Furthermore, previous studies that tried to estimate the generation-interval distributions from the observed serial intervals often ignored the differences between the incubation periods of infectors and those of infectees (e.g., \cite{klinkenberg2011correlation, ganyani2020estimating});

There is currently a need for better statistical tools for teasing apart the intrinsic generation-interval distributions from the observed serial intervals.

>>>>

Our study also demonstrates that there are multiple serial-interval distributions that correspond to the same set of generation-interval and incubation period distributions depending on their correlations;
all of them can provide the correct link between $r$--\RR (\fref{rR}).
Conversely, this means that not explicitly accounting for their correlations can bias the estimate of the intrinsic generation-interval distribution from the serial-interval distribution.
Furthermore, previous studies that tried to estimate the generation-interval distributions from the observed serial intervals often ignored the differences between the incubation periods of infectors and those of infectees (e.g., \cite{klinkenberg2011correlation, ganyani2020estimating});
There is currently a need for better statistical tools for teasing apart the intrinsic generation-interval distributions from the observed serial intervals.
